---
title: "simpleRegress"
author: "Tania Boror"
date: "4/3/2021"
output: 
    html_document:
      toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Bears Regression Model

### make a simple regression model - read in the data

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
newData <- data.frame(NECK=bears$NECK[c(5,15,23)])
predict(simp,newData)
predict(simp,newData,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


# HEADWIDTH
## Model LENGTH ~ HEADWTH

```{r}
headWid <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(headWid)
summary.lm(headWid)
```

# WEIGHT
## Model LENGTH ~ WEIGHT

```{r}
simpWT <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simpWT)
summary.lm(simpWT)
```

```{r}
new <- data.frame(WEIGHT=bears$WEIGHT [c(5, 15, 23)])
predict(simpWT,new,se.fit=TRUE)
```

# CHEST
##  Model LENGTH ~ CHEST

```{r}
simpCT <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simpCT)
summary.lm(simpCT)
```

```{r}
new <- data.frame(CHEST=bears$CHEST [c(5, 15, 23)])
predict(simpCT,new,se.fit=TRUE)
```
