---
title: "simpleRegress"
author: "Tania Boror"
date: "4/3/2021"
output: 
    html_document:
      toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Bears Regression Model

### make a simple regression model - read in the data

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
newData <- data.frame(NECK=bears$NECK[c(17,22,26)])
predict(simp,newData)
predict(simp,newData,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


# HEADWIDTH
## Model LENGTH ~ HEADWTH

```{r}
headWid <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(headWid)
summary.lm(headWid)
```

# HEADLENGTH
## Model LENGTH ~ HEADLEN

```{r}
simpHL <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simpHL)
summary.lm(simpHL)
```

```{r}
new <- data.frame(HEADLEN=bears$HEADLEN [c(5, 15, 23)])
predict(simpHL,new,se.fit=TRUE)
```

# WEIGHT

## Model LENGTH ~ WEIGHT

```{r}
simpWT <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simpWT)
summary.lm(simpWT)
```

```{r}
new <- data.frame(WEIGHT=bears$WEIGHT [c(5, 15, 23)])
predict(simpWT,new,se.fit=TRUE)
```

# CHEST
##  Model LENGTH ~ CHEST

```{r}
simpCT <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simpCT)
summary.lm(simpCT)
```

```{r}
new <- data.frame(CHEST=bears$CHEST [c(5, 15, 23)])
predict(simpCT,new,se.fit=TRUE)
```

# CONCLUSIONS

The best model is Length ~ HEADLEN as seen by the adjusted R-Squared the prediction of the length for bears 5, 15, and 23. These were:

70.31,  51.94, 58.83


The actual lengths of the bears were

`r bears$LENGTH[c(5, 15, 23)]` 

The error in prediction for bear number 5 was about 8 inches, for bear number 15, the prediction is right on, and for bear number 23, the error in the prediction was just under 6 inches.
